A planetary collision afterglow and transit of the resultant debris cloud

### 2023-10-09 src/tex/ms.tex
[showyourwork] overleaf sync

\begin{thebibliography}{10}
\expandafter\ifx\csname url\endcsname\relax
  \def\url#1{\burl{#1}}\fi
\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
\providecommand{\bibinfo}[2]{#2}
\providecommand{\eprint}[2][]{\url{#2}}
\providecommand{\doi}[1]{\url{https://doi.org/#1}}
\bibcommenthead

\bibitem{Williams11}
\bibinfo{author}{{Williams}, J.~P.} \& \bibinfo{author}{{Cieza}, L.~A.}
\newblock \bibinfo{title}{{Protoplanetary Disks and Their Evolution}}.
\newblock \emph{\bibinfo{journal}{\araa}} \textbf{\bibinfo{volume}{49}},
  \bibinfo{pages}{67--117} (\bibinfo{year}{2011}).
\newblock \urlprefix\url{http://adsabs.harvard.edu/abs/2011ARA%26A..49...67W}.

\bibitem{Wyatt15}
\bibinfo{author}{{Wyatt}, M.~C.}, \bibinfo{author}{{Pani{\'c}}, O.},
  \bibinfo{author}{{Kennedy}, G.~M.} \& \bibinfo{author}{{Matr{\`a}}, L.}
\newblock \bibinfo{title}{{Five steps in the evolution from protoplanetary to
  debris disk}}.
\newblock \emph{\bibinfo{journal}{\apss}} \textbf{\bibinfo{volume}{357}},
  \bibinfo{pages}{103} (\bibinfo{year}{2015}).
\newblock
  \urlprefix\url{https://ui.adsabs.harvard.edu/abs/2015Ap&SS.357..103W}.

\bibitem{Hughes18}
\bibinfo{author}{{Hughes}, A.~M.}, \bibinfo{author}{{Duch{\^e}ne}, G.} \&
  \bibinfo{author}{{Matthews}, B.~C.}
\newblock \bibinfo{title}{{Debris Disks: Structure, Composition, and
  Variability}}.
\newblock \emph{\bibinfo{journal}{\araa}} \textbf{\bibinfo{volume}{56}},
  \bibinfo{pages}{541--591} (\bibinfo{year}{2018}).
\newblock
  \urlprefix\url{https://ui.adsabs.harvard.edu/abs/2018ARA&A..56..541H}.

\bibitem{2014Sci...345.1032M}
\bibinfo{author}{{Meng}, H. Y.~A.} \emph{et~al.}
\newblock \bibinfo{title}{{Large impacts around a solar-analog star in the era
  of terrestrial planet formation}}.
\newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{345}},
  \bibinfo{pages}{1032--1035} (\bibinfo{year}{2014}).
\newblock
  \urlprefix\url{https://ui.adsabs.harvard.edu/abs/2014Sci...345.1032M}.

\bibitem{Su19}
\bibinfo{author}{{Su}, K. Y.~L.} \emph{et~al.}
\newblock \bibinfo{title}{{Extreme Debris Disk Variability: Exploring the
  Diverse Outcomes of Large Asteroid Impacts During the Era of Terrestrial
  Planet Formation}}.
\newblock \emph{\bibinfo{journal}{\aj}} \textbf{\bibinfo{volume}{157}},
  \bibinfo{pages}{202} (\bibinfo{year}{2019}).
\newblock
  \urlprefix\url{https://ui.adsabs.harvard.edu/abs/2019AJ....157..202S}.

\bibitem{Su22}
\bibinfo{author}{{Su}, K. Y.~L.}, \bibinfo{author}{{Kennedy}, G.~M.},
  \bibinfo{author}{{Schlawin}, E.}, \bibinfo{author}{{Jackson}, A.~P.} \&
  \bibinfo{author}{{Rieke}, G.~H.}
\newblock \bibinfo{title}{{A Star-sized Impact-produced Dust Clump in the
  Terrestrial Zone of the HD 166191 System}}.
\newblock \emph{\bibinfo{journal}{\apj}} \textbf{\bibinfo{volume}{927}},
  \bibinfo{pages}{135} (\bibinfo{year}{2022}).
\newblock
  \urlprefix\url{https://ui.adsabs.harvard.edu/abs/2022ApJ...927..135S}.

\bibitem{2021ApJ...918...71R}
\bibinfo{author}{{Rieke}, G.~H.}, \bibinfo{author}{{Su}, K.~Y.~L.},
  \bibinfo{author}{{Melis}, C.} \& \bibinfo{author}{{G{\'a}sp{\'a}r}, A.}
\newblock \bibinfo{title}{{Extreme Variability of the V488 Persei Debris
  Disk}}.
\newblock \emph{\bibinfo{journal}{\apj}} \textbf{\bibinfo{volume}{918}},
  \bibinfo{pages}{71} (\bibinfo{year}{2021}).

\bibitem{RizzoSmith21}
\bibinfo{author}{{Rizzo Smith}, M.} \emph{et~al.}
\newblock \bibinfo{title}{{ASASSN-21qj: A Rapidly Fading, Sun-Like Star}}.
\newblock \emph{\bibinfo{journal}{The Astronomer's Telegram}}
  \textbf{\bibinfo{volume}{14879}}, \bibinfo{pages}{1} (\bibinfo{year}{2021}).
\newblock
  \urlprefix\url{https://ui.adsabs.harvard.edu/abs/2021ATel14879....1R}.

\bibitem{RizzoSmith22}
\bibinfo{author}{{Rizzo Smith}, M.} \emph{et~al.}
\newblock \bibinfo{title}{{An Update on ASASSN-21qj: A Rapidly Fading, Sun-Like
  Star; Back With a Vengeance}}.
\newblock \emph{\bibinfo{journal}{The Astronomer's Telegram}}
  \textbf{\bibinfo{volume}{15531}}, \bibinfo{pages}{1} (\bibinfo{year}{2022}).
\newblock
  \urlprefix\url{https://ui.adsabs.harvard.edu/abs/2022ATel15531....1R}.

\bibitem{shappee_man_2014}
\bibinfo{author}{Shappee, B.~J.} \emph{et~al.}
\newblock \bibinfo{title}{The {Man} behind the {Curtain}: {X}-{Rays} {Drive}
  the {UV} through {NIR} {Variability} in the 2013 {Active} {Galactic}
  {Nucleus} {Outburst} in {NGC} 2617}.
\newblock \emph{\bibinfo{journal}{\apj}} \textbf{\bibinfo{volume}{788}},
  \bibinfo{pages}{48} (\bibinfo{year}{2014}).
\newblock \urlprefix\url{http://adsabs.harvard.edu/abs/2014ApJ...788...48S}.

\bibitem{kochanek_all-sky_2017}
\bibinfo{author}{Kochanek, C.~S.} \emph{et~al.}
\newblock \bibinfo{title}{The {All}-{Sky} {Automated} {Survey} for {Supernovae}
  ({ASAS}-{SN}) {Light} {Curve} {Server} v1.0}.
\newblock \emph{\bibinfo{journal}{Publications of the Astronomical Society of
  the Pacific}} \textbf{\bibinfo{volume}{129}}, \bibinfo{pages}{104502}
  (\bibinfo{year}{2017}).
\newblock \urlprefix\url{http://adsabs.harvard.edu/abs/2017PASP..129j4502K}.

\bibitem{Lock2017}
\bibinfo{author}{Lock, S.~J.} \& \bibinfo{author}{Stewart, S.~T.}
\newblock \bibinfo{title}{The structure of terrestrial bodies: {Impact}
  heating, corotation limits, and synestias}.
\newblock \emph{\bibinfo{journal}{Journal of Geophysical Research: Planets}}
  \textbf{\bibinfo{volume}{122}}, \bibinfo{pages}{950--982}
  (\bibinfo{year}{2017}).
\newblock \urlprefix\url{http://doi.wiley.com/10.1002/2016JE005239}.

\bibitem{2009ApJ...704..770M}
\bibinfo{author}{{Miller-Ricci}, E.}, \bibinfo{author}{{Meyer}, M.~R.},
  \bibinfo{author}{{Seager}, S.} \& \bibinfo{author}{{Elkins-Tanton}, L.}
\newblock \bibinfo{title}{{On the Emergent Spectra of Hot Protoplanet Collision
  Afterglows}}.
\newblock \emph{\bibinfo{journal}{\apj}} \textbf{\bibinfo{volume}{704}},
  \bibinfo{pages}{770--780} (\bibinfo{year}{2009}).

\bibitem{Schlichting2018a}
\bibinfo{author}{Schlichting, H.~E.}
\newblock \bibinfo{title}{ in \textit{Formation of super-{Earths}}} (eds
  \bibinfo{editor}{Hans, D.} \& \bibinfo{editor}{Belmonte, J.~A.})
  \emph{\bibinfo{booktitle}{Handbook of {Exoplanets}}}
  (\bibinfo{publisher}{Springer}, \bibinfo{year}{2018}).
\newblock \urlprefix\url{http://arxiv.org/abs/1802.03090}.
\newblock \bibinfo{note}{ArXiv: 1802.03090}.

\bibitem{DAngelo2018}
\bibinfo{author}{D’Angelo, G.} \& \bibinfo{author}{Lissauer, J.~J.}
\newblock \bibinfo{title}{ in \textit{Formation of {Giant} {Planets}}} (eds
  \bibinfo{editor}{Deeg, H.~J.} \& \bibinfo{editor}{Belmonte, J.~A.})
  \emph{\bibinfo{booktitle}{Handbook of {Exoplanets}}} \bibinfo{pages}{1--25}
  (\bibinfo{publisher}{Springer International Publishing},
  \bibinfo{address}{Cham}, \bibinfo{year}{2018}).
\newblock \urlprefix\url{https://doi.org/10.1007/978-3-319-30648-3_140-2}.

\bibitem{Kaib2016}
\bibinfo{author}{Kaib, N.~A.} \& \bibinfo{author}{Chambers, J.~E.}
\newblock \bibinfo{title}{The fragility of the terrestrial planets during a
  giant-planet instability}.
\newblock \emph{\bibinfo{journal}{\mnras}} \textbf{\bibinfo{volume}{455}},
  \bibinfo{pages}{3561--3569} (\bibinfo{year}{2016}).
\newblock \urlprefix\url{https://doi.org/10.1093/mnras/stv2554}.

\bibitem{Nakajima2015}
\bibinfo{author}{Nakajima, M.} \& \bibinfo{author}{Stevenson, D.~J.}
\newblock \bibinfo{title}{Melting and mixing states of the {Earth}'s mantle
  after the {Moon}-forming impact}.
\newblock \emph{\bibinfo{journal}{Earth and Planetary Science Letters}}
  \textbf{\bibinfo{volume}{427}}, \bibinfo{pages}{286--295}
  (\bibinfo{year}{2015}).
\newblock
  \urlprefix\url{http://www.sciencedirect.com/science/article/pii/S0012821X15003805}.

\bibitem{Carter2020}
\bibinfo{author}{Carter, P.~J.}, \bibinfo{author}{Lock, S.~J.} \&
  \bibinfo{author}{Stewart, S.~T.}
\newblock \bibinfo{title}{The {Energy} {Budgets} of {Giant} {Impacts}}.
\newblock \emph{\bibinfo{journal}{Journal of Geophysical Research: Planets}}
  \textbf{\bibinfo{volume}{125}} (\bibinfo{year}{2020}).
\newblock \bibinfo{note}{ArXiv: 1912.04936}.

\bibitem{Canup2001}
\bibinfo{author}{Canup, R.~M.} \& \bibinfo{author}{Asphaug, E.}
\newblock \bibinfo{title}{Origin of the {Moon} in a giant impact near the end
  of the {Earth}'s formation}.
\newblock \emph{\bibinfo{journal}{Nature}} \textbf{\bibinfo{volume}{412}},
  \bibinfo{pages}{708--12} (\bibinfo{year}{2001}).
\newblock \urlprefix\url{http://dx.doi.org/10.1038/35089010}.

\bibitem{Lock18}
\bibinfo{author}{{Lock}, S.~J.} \emph{et~al.}
\newblock \bibinfo{title}{{The Origin of the Moon Within a Terrestrial
  Synestia}}.
\newblock \emph{\bibinfo{journal}{Journal of Geophysical Research (Planets)}}
  \textbf{\bibinfo{volume}{123}}, \bibinfo{pages}{910--951}
  (\bibinfo{year}{2018}).
\newblock
  \urlprefix\url{https://ui.adsabs.harvard.edu/abs/2018JGRE..123..910L}.

\bibitem{Benz2008_Mercury_book}
\bibinfo{author}{Benz, W.}, \bibinfo{author}{Anic, A.},
  \bibinfo{author}{Horner, J.} \& \bibinfo{author}{Whitby, J.~A.}
\newblock \bibinfo{title}{ in \textit{The {Origin} of {Mercury}}} (eds
  \bibinfo{editor}{Balogh, A.}, \bibinfo{editor}{Ksanfomality, L.} \&
  \bibinfo{editor}{von Steiger, R.}) \emph{\bibinfo{booktitle}{Mercury}} Space
  {Sciences} {Series} of {ISSI}, \bibinfo{pages}{7--20}
  (\bibinfo{publisher}{Springer}, \bibinfo{address}{New York, NY},
  \bibinfo{year}{2008}).
\newblock \urlprefix\url{https://doi.org/10.1007/978-0-387-77539-5_2}.

\bibitem{Leinhardt2015}
\bibinfo{author}{Leinhardt, Z.~M.}, \bibinfo{author}{Dobinson, J.},
  \bibinfo{author}{Carter, P.~J.} \& \bibinfo{author}{Lines, S.}
\newblock \bibinfo{title}{Numerically predicted indirect signatures of
  terrestrial planet formation}.
\newblock \emph{\bibinfo{journal}{\apj}} \textbf{\bibinfo{volume}{806}},
  \bibinfo{pages}{23} (\bibinfo{year}{2015}).
\newblock \urlprefix\url{https://doi.org/10.1088/0004-637X/806/1/23}.

\bibitem{Carter2020a}
\bibinfo{author}{Carter, P.~J.} \& \bibinfo{author}{Stewart, S.~T.}
\newblock \bibinfo{title}{Colliding in the {Shadows} of {Giants}:
  {Planetesimal} {Collisions} during the {Growth} and {Migration} of {Gas}
  {Giants}}.
\newblock \emph{\bibinfo{journal}{The Planetary Science Journal}}
  \textbf{\bibinfo{volume}{1}}, \bibinfo{pages}{45} (\bibinfo{year}{2020}).
\newblock \urlprefix\url{https://doi.org/10.3847/PSJ/abaecc}.
\newblock \bibinfo{note}{ArXiv: 2008.05549 Publisher: IOP Publishing}.

\bibitem{Stewart2008}
\bibinfo{author}{Stewart, S.~T.}, \bibinfo{author}{Seifter, A.} \&
  \bibinfo{author}{Obst, A.~W.}
\newblock \bibinfo{title}{Shocked {H2O} ice: {Thermal} emission measurements
  and the criteria for phase changes during impact events}.
\newblock \emph{\bibinfo{journal}{Geophysical Research Letters}}
  \textbf{\bibinfo{volume}{35}}, \bibinfo{pages}{L23203}
  (\bibinfo{year}{2008}).
\newblock \urlprefix\url{http://doi.wiley.com/10.1029/2008GL035947}.
\newblock \bibinfo{note}{ISBN: 0094-8276}.

\bibitem{Davies2020}
\bibinfo{author}{Davies, E.~J.} \emph{et~al.}
\newblock \bibinfo{title}{Silicate {Melting} and {Vaporization} {During}
  {Rocky} {Planet} {Formation}}.
\newblock \emph{\bibinfo{journal}{Journal of Geophysical Research: Planets}}
  \textbf{\bibinfo{volume}{125}} (\bibinfo{year}{2020}).
\newblock
  \urlprefix\url{https://onlinelibrary.wiley.com/doi/abs/10.1029/2019JE006227}.
\newblock \bibinfo{note}{ArXiv: 2002.00998 Publisher: John Wiley \& Sons, Ltd}.

\bibitem{Johnson2015}
\bibinfo{author}{Johnson, B.~C.}, \bibinfo{author}{Minton, D.~A.},
  \bibinfo{author}{Melosh, H.~J.} \& \bibinfo{author}{Zuber, M.~T.}
\newblock \bibinfo{title}{Impact jetting as the origin of chondrules}.
\newblock \emph{\bibinfo{journal}{Nature}} \textbf{\bibinfo{volume}{517}},
  \bibinfo{pages}{339--341} (\bibinfo{year}{2015}).
\newblock \urlprefix\url{http://dx.doi.org/10.1038/nature14105}.
\newblock \bibinfo{note}{Publisher: Nature Publishing Group, a division of
  Macmillan Publishers Limited. All Rights Reserved.}

\bibitem{Caracas2023}
\bibinfo{author}{Caracas, R.} \& \bibinfo{author}{Stewart, S.~T.}
\newblock \bibinfo{title}{No magma ocean surface after giant impacts between
  rocky planets}.
\newblock \emph{\bibinfo{journal}{Earth and Planetary Science Letters}}
  \textbf{\bibinfo{volume}{608}}, \bibinfo{pages}{118014}
  (\bibinfo{year}{2023}).
\newblock
  \urlprefix\url{https://www.sciencedirect.com/science/article/pii/S0012821X23000274}.

\bibitem{Fegley2023_BSE_cond}
\bibinfo{author}{Fegley, B.}, \bibinfo{author}{Lodders, K.} \&
  \bibinfo{author}{Jacobson, N.~S.}
\newblock \bibinfo{title}{Chemical equilibrium calculations for bulk silicate
  earth material at high temperatures}.
\newblock \emph{\bibinfo{journal}{Geochemistry}} \bibinfo{pages}{125961}
  (\bibinfo{year}{2023}).
\newblock
  \urlprefix\url{https://www.sciencedirect.com/science/article/pii/S0009281923000120}.

>>>>

% \begin{thebibliography}{10}
% \expandafter\ifx\csname url\endcsname\relax
%   \def\url#1{\burl{#1}}\fi
% \expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
% \providecommand{\bibinfo}[2]{#2}
% \providecommand{\eprint}[2][]{\url{#2}}
% \providecommand{\doi}[1]{\url{https://doi.org/#1}}
% \bibcommenthead

% \bibitem{Williams11}
% \bibinfo{author}{{Williams}, J.~P.} \& \bibinfo{author}{{Cieza}, L.~A.}
% \newblock \bibinfo{title}{{Protoplanetary Disks and Their Evolution}}.
% \newblock \emph{\bibinfo{journal}{\araa}} \textbf{\bibinfo{volume}{49}},
%   \bibinfo{pages}{67--117} (\bibinfo{year}{2011}).
% \newblock \urlprefix\url{http://adsabs.harvard.edu/abs/2011ARA%26A..49...67W}.

% \bibitem{Wyatt15}
% \bibinfo{author}{{Wyatt}, M.~C.}, \bibinfo{author}{{Pani{\'c}}, O.},
%   \bibinfo{author}{{Kennedy}, G.~M.} \& \bibinfo{author}{{Matr{\`a}}, L.}
% \newblock \bibinfo{title}{{Five steps in the evolution from protoplanetary to
%   debris disk}}.
% \newblock \emph{\bibinfo{journal}{\apss}} \textbf{\bibinfo{volume}{357}},
%   \bibinfo{pages}{103} (\bibinfo{year}{2015}).
% \newblock
%   \urlprefix\url{https://ui.adsabs.harvard.edu/abs/2015Ap&SS.357..103W}.

% \bibitem{Hughes18}
% \bibinfo{author}{{Hughes}, A.~M.}, \bibinfo{author}{{Duch{\^e}ne}, G.} \&
%   \bibinfo{author}{{Matthews}, B.~C.}
% \newblock \bibinfo{title}{{Debris Disks: Structure, Composition, and
%   Variability}}.
% \newblock \emph{\bibinfo{journal}{\araa}} \textbf{\bibinfo{volume}{56}},
%   \bibinfo{pages}{541--591} (\bibinfo{year}{2018}).
% \newblock
%   \urlprefix\url{https://ui.adsabs.harvard.edu/abs/2018ARA&A..56..541H}.

% \bibitem{2014Sci...345.1032M}
% \bibinfo{author}{{Meng}, H. Y.~A.} \emph{et~al.}
% \newblock \bibinfo{title}{{Large impacts around a solar-analog star in the era
%   of terrestrial planet formation}}.
% \newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{345}},
%   \bibinfo{pages}{1032--1035} (\bibinfo{year}{2014}).
% \newblock
%   \urlprefix\url{https://ui.adsabs.harvard.edu/abs/2014Sci...345.1032M}.

% \bibitem{Su19}
% \bibinfo{author}{{Su}, K. Y.~L.} \emph{et~al.}
% \newblock \bibinfo{title}{{Extreme Debris Disk Variability: Exploring the
%   Diverse Outcomes of Large Asteroid Impacts During the Era of Terrestrial
%   Planet Formation}}.
% \newblock \emph{\bibinfo{journal}{\aj}} \textbf{\bibinfo{volume}{157}},
%   \bibinfo{pages}{202} (\bibinfo{year}{2019}).
% \newblock
%   \urlprefix\url{https://ui.adsabs.harvard.edu/abs/2019AJ....157..202S}.

% \bibitem{Su22}
% \bibinfo{author}{{Su}, K. Y.~L.}, \bibinfo{author}{{Kennedy}, G.~M.},
%   \bibinfo{author}{{Schlawin}, E.}, \bibinfo{author}{{Jackson}, A.~P.} \&
%   \bibinfo{author}{{Rieke}, G.~H.}
% \newblock \bibinfo{title}{{A Star-sized Impact-produced Dust Clump in the
%   Terrestrial Zone of the HD 166191 System}}.
% \newblock \emph{\bibinfo{journal}{\apj}} \textbf{\bibinfo{volume}{927}},
%   \bibinfo{pages}{135} (\bibinfo{year}{2022}).
% \newblock
%   \urlprefix\url{https://ui.adsabs.harvard.edu/abs/2022ApJ...927..135S}.

% \bibitem{2021ApJ...918...71R}
% \bibinfo{author}{{Rieke}, G.~H.}, \bibinfo{author}{{Su}, K.~Y.~L.},
%   \bibinfo{author}{{Melis}, C.} \& \bibinfo{author}{{G{\'a}sp{\'a}r}, A.}
% \newblock \bibinfo{title}{{Extreme Variability of the V488 Persei Debris
%   Disk}}.
% \newblock \emph{\bibinfo{journal}{\apj}} \textbf{\bibinfo{volume}{918}},
%   \bibinfo{pages}{71} (\bibinfo{year}{2021}).

% \bibitem{RizzoSmith21}
% \bibinfo{author}{{Rizzo Smith}, M.} \emph{et~al.}
% \newblock \bibinfo{title}{{ASASSN-21qj: A Rapidly Fading, Sun-Like Star}}.
% \newblock \emph{\bibinfo{journal}{The Astronomer's Telegram}}
%   \textbf{\bibinfo{volume}{14879}}, \bibinfo{pages}{1} (\bibinfo{year}{2021}).
% \newblock
%   \urlprefix\url{https://ui.adsabs.harvard.edu/abs/2021ATel14879....1R}.

% \bibitem{RizzoSmith22}
% \bibinfo{author}{{Rizzo Smith}, M.} \emph{et~al.}
% \newblock \bibinfo{title}{{An Update on ASASSN-21qj: A Rapidly Fading, Sun-Like
%   Star; Back With a Vengeance}}.
% \newblock \emph{\bibinfo{journal}{The Astronomer's Telegram}}
%   \textbf{\bibinfo{volume}{15531}}, \bibinfo{pages}{1} (\bibinfo{year}{2022}).
% \newblock
%   \urlprefix\url{https://ui.adsabs.harvard.edu/abs/2022ATel15531....1R}.

% \bibitem{shappee_man_2014}
% \bibinfo{author}{Shappee, B.~J.} \emph{et~al.}
% \newblock \bibinfo{title}{The {Man} behind the {Curtain}: {X}-{Rays} {Drive}
%   the {UV} through {NIR} {Variability} in the 2013 {Active} {Galactic}
%   {Nucleus} {Outburst} in {NGC} 2617}.
% \newblock \emph{\bibinfo{journal}{\apj}} \textbf{\bibinfo{volume}{788}},
%   \bibinfo{pages}{48} (\bibinfo{year}{2014}).
% \newblock \urlprefix\url{http://adsabs.harvard.edu/abs/2014ApJ...788...48S}.

% \bibitem{kochanek_all-sky_2017}
% \bibinfo{author}{Kochanek, C.~S.} \emph{et~al.}
% \newblock \bibinfo{title}{The {All}-{Sky} {Automated} {Survey} for {Supernovae}
%   ({ASAS}-{SN}) {Light} {Curve} {Server} v1.0}.
% \newblock \emph{\bibinfo{journal}{Publications of the Astronomical Society of
%   the Pacific}} \textbf{\bibinfo{volume}{129}}, \bibinfo{pages}{104502}
%   (\bibinfo{year}{2017}).
% \newblock \urlprefix\url{http://adsabs.harvard.edu/abs/2017PASP..129j4502K}.

% \bibitem{Lock2017}
% \bibinfo{author}{Lock, S.~J.} \& \bibinfo{author}{Stewart, S.~T.}
% \newblock \bibinfo{title}{The structure of terrestrial bodies: {Impact}
%   heating, corotation limits, and synestias}.
% \newblock \emph{\bibinfo{journal}{Journal of Geophysical Research: Planets}}
%   \textbf{\bibinfo{volume}{122}}, \bibinfo{pages}{950--982}
%   (\bibinfo{year}{2017}).
% \newblock \urlprefix\url{http://doi.wiley.com/10.1002/2016JE005239}.

% \bibitem{2009ApJ...704..770M}
% \bibinfo{author}{{Miller-Ricci}, E.}, \bibinfo{author}{{Meyer}, M.~R.},
%   \bibinfo{author}{{Seager}, S.} \& \bibinfo{author}{{Elkins-Tanton}, L.}
% \newblock \bibinfo{title}{{On the Emergent Spectra of Hot Protoplanet Collision
%   Afterglows}}.
% \newblock \emph{\bibinfo{journal}{\apj}} \textbf{\bibinfo{volume}{704}},
%   \bibinfo{pages}{770--780} (\bibinfo{year}{2009}).

% \bibitem{Schlichting2018a}
% \bibinfo{author}{Schlichting, H.~E.}
% \newblock \bibinfo{title}{ in \textit{Formation of super-{Earths}}} (eds
%   \bibinfo{editor}{Hans, D.} \& \bibinfo{editor}{Belmonte, J.~A.})
%   \emph{\bibinfo{booktitle}{Handbook of {Exoplanets}}}
%   (\bibinfo{publisher}{Springer}, \bibinfo{year}{2018}).
% \newblock \urlprefix\url{http://arxiv.org/abs/1802.03090}.
% \newblock \bibinfo{note}{ArXiv: 1802.03090}.

% \bibitem{DAngelo2018}
% \bibinfo{author}{D’Angelo, G.} \& \bibinfo{author}{Lissauer, J.~J.}
% \newblock \bibinfo{title}{ in \textit{Formation of {Giant} {Planets}}} (eds
%   \bibinfo{editor}{Deeg, H.~J.} \& \bibinfo{editor}{Belmonte, J.~A.})
%   \emph{\bibinfo{booktitle}{Handbook of {Exoplanets}}} \bibinfo{pages}{1--25}
%   (\bibinfo{publisher}{Springer International Publishing},
%   \bibinfo{address}{Cham}, \bibinfo{year}{2018}).
% \newblock \urlprefix\url{https://doi.org/10.1007/978-3-319-30648-3_140-2}.

% \bibitem{Kaib2016}
% \bibinfo{author}{Kaib, N.~A.} \& \bibinfo{author}{Chambers, J.~E.}
% \newblock \bibinfo{title}{The fragility of the terrestrial planets during a
%   giant-planet instability}.
% \newblock \emph{\bibinfo{journal}{\mnras}} \textbf{\bibinfo{volume}{455}},
%   \bibinfo{pages}{3561--3569} (\bibinfo{year}{2016}).
% \newblock \urlprefix\url{https://doi.org/10.1093/mnras/stv2554}.

% \bibitem{Nakajima2015}
% \bibinfo{author}{Nakajima, M.} \& \bibinfo{author}{Stevenson, D.~J.}
% \newblock \bibinfo{title}{Melting and mixing states of the {Earth}'s mantle
%   after the {Moon}-forming impact}.
% \newblock \emph{\bibinfo{journal}{Earth and Planetary Science Letters}}
%   \textbf{\bibinfo{volume}{427}}, \bibinfo{pages}{286--295}
%   (\bibinfo{year}{2015}).
% \newblock
%   \urlprefix\url{http://www.sciencedirect.com/science/article/pii/S0012821X15003805}.

% \bibitem{Carter2020}
% \bibinfo{author}{Carter, P.~J.}, \bibinfo{author}{Lock, S.~J.} \&
%   \bibinfo{author}{Stewart, S.~T.}
% \newblock \bibinfo{title}{The {Energy} {Budgets} of {Giant} {Impacts}}.
% \newblock \emph{\bibinfo{journal}{Journal of Geophysical Research: Planets}}
%   \textbf{\bibinfo{volume}{125}} (\bibinfo{year}{2020}).
% \newblock \bibinfo{note}{ArXiv: 1912.04936}.

% \bibitem{Canup2001}
% \bibinfo{author}{Canup, R.~M.} \& \bibinfo{author}{Asphaug, E.}
% \newblock \bibinfo{title}{Origin of the {Moon} in a giant impact near the end
%   of the {Earth}'s formation}.
% \newblock \emph{\bibinfo{journal}{Nature}} \textbf{\bibinfo{volume}{412}},
%   \bibinfo{pages}{708--12} (\bibinfo{year}{2001}).
% \newblock \urlprefix\url{http://dx.doi.org/10.1038/35089010}.

% \bibitem{Lock18}
% \bibinfo{author}{{Lock}, S.~J.} \emph{et~al.}
% \newblock \bibinfo{title}{{The Origin of the Moon Within a Terrestrial
%   Synestia}}.
% \newblock \emph{\bibinfo{journal}{Journal of Geophysical Research (Planets)}}
%   \textbf{\bibinfo{volume}{123}}, \bibinfo{pages}{910--951}
%   (\bibinfo{year}{2018}).
% \newblock
%   \urlprefix\url{https://ui.adsabs.harvard.edu/abs/2018JGRE..123..910L}.

% \bibitem{Benz2008_Mercury_book}
% \bibinfo{author}{Benz, W.}, \bibinfo{author}{Anic, A.},
%   \bibinfo{author}{Horner, J.} \& \bibinfo{author}{Whitby, J.~A.}
% \newblock \bibinfo{title}{ in \textit{The {Origin} of {Mercury}}} (eds
%   \bibinfo{editor}{Balogh, A.}, \bibinfo{editor}{Ksanfomality, L.} \&
%   \bibinfo{editor}{von Steiger, R.}) \emph{\bibinfo{booktitle}{Mercury}} Space
%   {Sciences} {Series} of {ISSI}, \bibinfo{pages}{7--20}
%   (\bibinfo{publisher}{Springer}, \bibinfo{address}{New York, NY},
%   \bibinfo{year}{2008}).
% \newblock \urlprefix\url{https://doi.org/10.1007/978-0-387-77539-5_2}.

% \bibitem{Leinhardt2015}
% \bibinfo{author}{Leinhardt, Z.~M.}, \bibinfo{author}{Dobinson, J.},
%   \bibinfo{author}{Carter, P.~J.} \& \bibinfo{author}{Lines, S.}
% \newblock \bibinfo{title}{Numerically predicted indirect signatures of
%   terrestrial planet formation}.
% \newblock \emph{\bibinfo{journal}{\apj}} \textbf{\bibinfo{volume}{806}},
%   \bibinfo{pages}{23} (\bibinfo{year}{2015}).
% \newblock \urlprefix\url{https://doi.org/10.1088/0004-637X/806/1/23}.

% \bibitem{Carter2020a}
% \bibinfo{author}{Carter, P.~J.} \& \bibinfo{author}{Stewart, S.~T.}
% \newblock \bibinfo{title}{Colliding in the {Shadows} of {Giants}:
%   {Planetesimal} {Collisions} during the {Growth} and {Migration} of {Gas}
%   {Giants}}.
% \newblock \emph{\bibinfo{journal}{The Planetary Science Journal}}
%   \textbf{\bibinfo{volume}{1}}, \bibinfo{pages}{45} (\bibinfo{year}{2020}).
% \newblock \urlprefix\url{https://doi.org/10.3847/PSJ/abaecc}.
% \newblock \bibinfo{note}{ArXiv: 2008.05549 Publisher: IOP Publishing}.

% \bibitem{Stewart2008}
% \bibinfo{author}{Stewart, S.~T.}, \bibinfo{author}{Seifter, A.} \&
%   \bibinfo{author}{Obst, A.~W.}
% \newblock \bibinfo{title}{Shocked {H2O} ice: {Thermal} emission measurements
%   and the criteria for phase changes during impact events}.
% \newblock \emph{\bibinfo{journal}{Geophysical Research Letters}}
%   \textbf{\bibinfo{volume}{35}}, \bibinfo{pages}{L23203}
%   (\bibinfo{year}{2008}).
% \newblock \urlprefix\url{http://doi.wiley.com/10.1029/2008GL035947}.
% \newblock \bibinfo{note}{ISBN: 0094-8276}.

% \bibitem{Davies2020}
% \bibinfo{author}{Davies, E.~J.} \emph{et~al.}
% \newblock \bibinfo{title}{Silicate {Melting} and {Vaporization} {During}
%   {Rocky} {Planet} {Formation}}.
% \newblock \emph{\bibinfo{journal}{Journal of Geophysical Research: Planets}}
%   \textbf{\bibinfo{volume}{125}} (\bibinfo{year}{2020}).
% \newblock
%   \urlprefix\url{https://onlinelibrary.wiley.com/doi/abs/10.1029/2019JE006227}.
% \newblock \bibinfo{note}{ArXiv: 2002.00998 Publisher: John Wiley \& Sons, Ltd}.

% \bibitem{Johnson2015}
% \bibinfo{author}{Johnson, B.~C.}, \bibinfo{author}{Minton, D.~A.},
%   \bibinfo{author}{Melosh, H.~J.} \& \bibinfo{author}{Zuber, M.~T.}
% \newblock \bibinfo{title}{Impact jetting as the origin of chondrules}.
% \newblock \emph{\bibinfo{journal}{Nature}} \textbf{\bibinfo{volume}{517}},
%   \bibinfo{pages}{339--341} (\bibinfo{year}{2015}).
% \newblock \urlprefix\url{http://dx.doi.org/10.1038/nature14105}.
% \newblock \bibinfo{note}{Publisher: Nature Publishing Group, a division of
%   Macmillan Publishers Limited. All Rights Reserved.}

% \bibitem{Caracas2023}
% \bibinfo{author}{Caracas, R.} \& \bibinfo{author}{Stewart, S.~T.}
% \newblock \bibinfo{title}{No magma ocean surface after giant impacts between
%   rocky planets}.
% \newblock \emph{\bibinfo{journal}{Earth and Planetary Science Letters}}
%   \textbf{\bibinfo{volume}{608}}, \bibinfo{pages}{118014}
%   (\bibinfo{year}{2023}).
% \newblock
%   \urlprefix\url{https://www.sciencedirect.com/science/article/pii/S0012821X23000274}.

% \bibitem{Fegley2023_BSE_cond}
% \bibinfo{author}{Fegley, B.}, \bibinfo{author}{Lodders, K.} \&
%   \bibinfo{author}{Jacobson, N.~S.}
% \newblock \bibinfo{title}{Chemical equilibrium calculations for bulk silicate
%   earth material at high temperatures}.
% \newblock \emph{\bibinfo{journal}{Geochemistry}} \bibinfo{pages}{125961}
%   (\bibinfo{year}{2023}).
% \newblock
%   \urlprefix\url{https://www.sciencedirect.com/science/article/pii/S0009281923000120}.
